Discovery of Rotational Modulations in the Planetary-mass Companion 2M1207\lowercase{b}: An intermediate Rotation Period and Heterogeneous Clouds in a Low Gravity Atmosphere

### 2015-09-25 summary/submission/ms.tex
submitted

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mbox{Jup}}$}
\begin{document}

@@

\begin{figure*}
  \centering
  \plottwo{original}{subtracted}
  \caption{Point spread function subtraction allows isolating the
    secondary and accurately measuring its brightness in our WFC3
    F160W images. {\em Upper}: original image, the position of 2M1207
    b is indicated by a white circle.  {\em Lower:} residual image --
    after the subtraction of the hybrid PSF, 2M1207b is detected at a
    high significance level.}
  \label{fig:1}
\end{figure*}

@@

Intensity modulations introduced by heterogeneous clouds can be
directly observed and studied via time resolved observation and
rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Burgasser2013,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
properties and obtained great success in determining the rotation
period and unveiling the structures of the atmosphere of brown dwarfs
. \citet{Kostov2013}
demonstrated that these techniques can be applied to directly imaged
exoplanets, too, allowing comparative studies of objects with
different surface gravities. However, high contrast magnifies the
challenges for directly imaged exoplanets and planetary-mass
companions to acquire high-precision light curves comparing to brown
dwarfs.

@@

In this {\em Letter} we present the first, high-contrast, high-cadence,
high-precision, time-resolved {\em Hubble Space Telescope} (HST)
photometric time series of 2M1207b, a directly imaged planetary-mass
object. We successfully detect rotational modulation and measure the
amplitudes in two bands and determine the rotational period. These
observations probe the spatial heterogeneity and vertical structure of
clouds in planetary mass objects for the first time.

@@

The major challenge of high contrast observation with WFC3/IR is the
fact that the detector is significantly under-sampled.  2M1207A and b
are only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF on the
detector. When applying roll subtraction, notable artifacts are
introduced by image shifting and interpolation.  \tinytim{} PSF
simulator \citep{Krist1995} offers a solution by providing Nyquist or
better sampled PSF, but systematic errors of \tinytim{} PSF for WFC3
limits its ability in high precision photometry \citep{Biretta2014}.
Building on the large number of PSFs obtained in our program at two
different roll angles, we followed a novel, two-step approach that
uses a hybrid PSF.  First, based on our observations, we derived
correction maps for \tinytim{} that accurately described the scattered
light component for the primary at the correct location on the
detector. Second, we carried out a PSF-photometry using hybrid PSFs
composed by \tinytim{} PSFs and the correction map by simultaneously
minimizing the residuals from the primary and the secondary.
% However, we are able to fully characterize the difference of model
% and observed PSFs with 6 orbits time-resolved observation data. To
% obtain robust \tinytim{} PSF photometry, we design a 2-round PSF
% fitting strategy: 1. calculating correction map for \tinytim{};
% 2. hybrid PSF photometry.

@@

% PSF profiles change with exposure positions due to
% pixelation, especially for the case that WFC3 IR is significantly
% under-sampled. Also, the flat fields may potentially have large scale
% structures \citep{dressel2012wide}. We find a correlation of
% photometry with PSF positions on detector frame for both 2M1207A and
% b. Correction is made by normalizing each group of
% exposures that have the same dithering position and telescope roll angle
% individually -- we take the median of the fluxes that are measured
% from these exposures as normalization factors and divided them from
% every photometric measurement. Because the normalization factor for
% each group of exposures is calculated across the whole observation in
% time domain,
% this step has negligible impacts on variability
% analysis.

@@

@@

 \begin{figure*}
  \centering
  \plotone{systematics}
  \caption{F125W (left) and F160W (right) light curves under different
    variability verification tests. Individual measurements are
    plotted with gray crosses. Photometric measurements of the same exposure
    sequence are binned, and binned photometry are plotted with points
    or squares. Best fitted sinusoids are plotted with solid
    lines. {\em Upper}: binned measurements taken in dithering
    position 1 and 3 (red points) and that taken in 2 and 4 (blue
    squares) are plotted with different symbols. They demonstrate same
    trend of modulation. In upper left panel, the green line a sinusoid
    fitted with all parameters freely varying, and the purple line is
    a sinusoid fitted with the period set the same as that of
    F125W. {\em Middle}: sinusoids fitted without using the
    data taken in Orbit \#1. These curves are almost identical to the
    curves plotted in upper panel. {\em Lower}: photometry measured
    with AFEM-added images and best fitted sinul curves. These
    points and curves are also almost identical to those plotted
    in the upper panel.}
  \label{fig:2}
\end{figure*}

@@

  \begin{figure*}
  \centering
  \plotone{sineCurveFit_binCombined}
  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
    with filter F125W (left) and F160W (right). Unbinned
  measurements are plotted in gray crosses and binned photometry are
  plotted with red points. Best fitted sinusoids are plotted
  with blue solid lines.}
  \label{fig:3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{periodDistr}
  \includegraphics[width=0.45\textwidth]{amplitudeDistr}
  \caption{Distributions for period (left) and amplitude (right) for the light
    curves of F125W and F160W. The bin sizes for the histograms of
    period  and amplitude are
  0.25 hours and 0.5\%, respectively. Histograms are
  normalized to the maxima. In the right panel, Gaussian profiles are fitted to the
  histograms and plotted in solid lines.}
  \label{fig:4}
\end{figure*}

@@

@@

\begin{figure*}
  \centering
  \plottwo{rotationDiagram}{JH}
  \caption{comparison of 2M1207's rotation period and color change
    with brown dwarfs, \bpic{} b, and solar system planets. {\em
      Left}: period vs. mass plot for 2M1207b (red square), solar
    system planets and \bpic{} b (blue squares), and brown dwarfs
    (black circles, gray shade). Final rotation rates for 2M1207b and
    \bpic{} b estimated based on conservation of angular momentum are
    plotted with faint red and blue squares, respectively. The mass of brown dwarfs are assumed
    to be 30 \mjup{}. The gray rectangle that has a $\pm$15 \mjup
    range in $x$, and a $\pm \sigma$ of brown dwarf periods range in
    $y$, indicates a region where brown dwarfs most likely to appear
    in this diagram. Rotation period monotonically decreases with the
    increase of mass. {\em Right}: ratio of modulation amplitude in J
    and H band vs. spectral type for 2M1207b and brown dwarfs. The
    point for 2M1207b is shifted to +$x$ for half spectral type for
    clarification.  The colors of the points represent J$-$H
    magnitude, and the sizes of the points are proportional to the
    J-band modulation amplitudes. The gray dashed line is the result
    of a linear fit to these points.  Correlation of J- and
    H-band modulation amplitude ratio and spectral type is shown.}
 \label{fig:5}
\end{figure*}

% A fundamental result of our study is the direct determination of the
% rotation period of a directly imaged planetary-mass object. We
% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
% brown dwarfs with well defined rotation period from the study of
% \cite{Metchev2015}, and compare their rotation velocities with solar
% system planets and \bpic{} b in the left
% panel of Figure \ref{fig:5}.  The study by
% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
% and demonstrated that it fits a trend defined by Solar System planets
% in which more massive planets have faster rotation rates. They suggested
% that this relation is linked to the accretion processes during planet
% formation.

An important result of our study is the direct measurement of the
photometric modulation period of a directly imaged planetary-mass
object. We infer the rotation period of 2M1207b to be the same as
the period of photometric variation. Although horizontal winds can cause the
measured period to differ from true rotation period, it is
unlikely that the difference is greater than the uncertainty of the
measurement, since for Jupiter and Saturn, typical wind speeds are
more than one order of magnitude smaller than the equatorial rotation speeds.
% Our
% inferred rotation period of 2M1207b is typical among those of brown dwarfs
% \citep{Reiners2008}.
In the left panel of Figure~\ref{fig:5} we
compare the rotation period of 2M1207b to the solar system planets,
\bpic{} b the only other directly imaged planet with an estimated
period and measured \vsini, and field brown dwarfs from the study of
\cite[][]{Metchev2015}. \citet[][]{Snellen2014} measured \vsini{} for
\bpic{} b and demonstrated that it fits a trend defined by Solar
System planets in which more massive planets have faster rotation
rates. The interesting finding that \bpic{} b, an exoplanet that
formed in a protoplanetary disk, follows this trend suggests a
possibly connection between planet mass, initial angular momentum, and
formation in a disk.

Excitingly, our measurement of the rotation period of 2M1207b, a
planet mass companion that has similar age to \bpic{} b, has a
rotation period that fits in the same trend, as well as majority of
the brown dwarfs. As 2M1207b and \bpic{} b evolve and cool down, they are
expected to shrink to the size of Jupiter. Order of magnitude
estimation based on the conservation of angular momentum results in
final rotation periods of $\sim 5$ h and $\sim 3$ hours
\citep{Snellen2014} for 2M1207b and \bpic{} b, respectively, which
still fit to the period vs. mass trend. Although 2M1207A is known to
host a circumsubstellar disk \citep{Sterzik2004}, the low mass of
typical brown dwarf disks \citep[e.g.]{Klein2003, Mohanty2013} and its
large separation argue against the possibility that 2M1207b has formed
in a protoplanetary disk.  The result that objects formed in different
scenarios share the same trend of period vs. mass suggests that
rotation periods -- in absence of well-determined ages -- may
contribute insufficient evidence for a formation in a disk vs. in a
cloud core environment. Although rotation rates may have limited value
for deciphering formation pathways, measurements of mass, age, and
rotation periods will map the angular momentum evolution of
planetary-mass objects and may place powerful constraints on the
evolution of the internal structures of these contracting objects.
%{\em Add younger BDs and this may change}
% Excitingly, our measurement of the rotation period demonstrates that
% 2M1207b, a planetary-mass companion  with similar age to \bpic{} b, has a rotation velocity
% that fits in the same trend, as well as majority of brown
% dwarfs. We note that 2M1207b is most likely formed in the same way as brown
% dwarfs by gravitational fragmentation, which suggests
% that rotation periods are not good tracers of the formation pathways
% and may not contribute important evidence for a formation in a disk
% vs. in a cloud core environment.

@@

% {\color{red}This trend can be qualitatively explained using the toy model proposed
% in \cite{Yang2014} within the spectral type range of mid-L to L-T
% transition. Assuming that intensity modulations are introduced by a
% refractory cloud whose upper layer locates at altitude $z$, the
% amplitude ratio for J and H band can be expressed as
% $\mathrm{Amp_{J}}/\mathrm{Amp_{H}} =
% \exp\left[-(\tau_{\mathrm{J}}(z)/\tau_{{\mathrm{H}}}(z)\right]$,
% where $\tau_{\mathrm{J}}(z)$ and $\tau_{\mathrm{H}}(z)$ are the
% optical depths of upper cloud layer for J and H bands. The opacity for
% J band is smaller than that for H, therefore from mid-L to L-T
% transition, as the cloud upper boundary appears higher in the
% atmosphere, the optical depth difference for the two bands gets
% smaller, and the amplitude ratio decreases.  We note, that the late T
% dwarf 2M2228 falls exactly on this trend, but whose variations are
% likely to emerge from a different mechanism as their silicate clouds
% are below the visible photosphere \citep[e.g.][]{Stephens2009}.

% We infer that the upper cloud layer of 2M1207b is at a similar optical
% depth as that of a matching spectral type field brown dwarf from the fact
% that they share similar J- and H-bands light curve amplitude ratio.
% The
% two processes that atmosphere opacity at certain pressure level
% enhances and the cloud thickness increases with the decrease of surface
% gravity have to counterbalance with each other to maintain the optical
% depth of the cloud upper layer.}

@@

Support for program number 13418 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the
Association of Universities for Research in Astronomy, Inc., under
NASA contract NAS5-26555. The results reported herein benefited from
collaborations and/or information exchange within NASA's Nexus for
Exoplanet System Science (NExSS) research coordination network
sponsored by NASA's Science Mission Directorate. M.S.M. acknowledges
support from the NASA Astrophysics Theory Program. A.P.S. acknowledges
support from NSF grant AST1313444.
\bibliography{ref.bib}
\end{document}

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
%\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mathrm{Jup}}$}
\begin{document}

@@

\begin{figure*}
\centering
  \plottwo{f1a}{f1b}
  \caption{Point spread function subtraction allows isolating the
    secondary and accurately measuring its brightness in our WFC3
    F160W images. {\em Upper}: original image, the position of 2M1207
    b is indicated by a white circle.  {\em Lower:} residual image --
    after the subtraction of the hybrid PSF, 2M1207b is detected at a
    high significance level.}
  \label{fig:1}
\end{figure*}

@@

Intensity modulations introduced by heterogeneous clouds can be
directly observed and studied via time resolved observation and
rotational mapping \citep[e.g.][]{Apai2013,Buenzli2012,Buenzli2015,Radigan2012,Yang2015,Metchev2015,Heinze2015}. These techniques isolate the effect of cloud
properties and obtained great success in determining the rotation
period and unveiling the structures of the atmosphere of brown dwarfs
. \citet{Kostov2013}
demonstrated that these techniques can be applied to directly imaged
exoplanets, too, allowing comparative studies of objects with
different surface gravities. However, high contrast magnifies the
challenges for directly imaged exoplanets and planetary-mass
companions to acquire high-precision light curves comparing to brown
dwarfs.

@@

In this {\em Paper} we present the first, high-contrast, high-cadence,
high-precision, time-resolved {\em Hubble Space Telescope} (HST)
photometric time series of 2M1207b, a directly imaged planetary-mass
object. We successfully detect rotational modulation and measure the
amplitudes in two bands and determine the rotational period. These
observations probe the spatial heterogeneity and vertical structure of
clouds in planetary mass objects for the first time.

@@

The major challenge of high contrast observation with WFC3/IR is the
fact that the detector is significantly under-sampled.  2M1207A and b
are only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF on the
detector. When applying roll subtraction, notable artifacts are
introduced by image shifting and interpolation.  \tinytim{} PSF
simulator \citep{Krist1995} offers a solution by providing Nyquist or
better sampled PSF, but systematic errors of \tinytim{} PSF for WFC3
limits its ability in high precision photometry \citep{Biretta2014}.
Building on the large number of PSFs obtained in our program at two
different roll angles, we followed a novel, two-step approach that
uses a hybrid PSF.  First, based on our observations, we derived
correction maps for \tinytim{} that accurately described the scattered
light component for the primary at the correct location on the
detector. Second, we carried out a PSF-photometry using hybrid PSFs
composed by \tinytim{} PSFs and the correction map by simultaneously
minimizing the residuals from the primary and the secondary.

@@

@@

\begin{figure*}
  \centering
  \plotone{f2}
  \caption{F125W (left) and F160W (right) light curves under different
    variability verification tests. Individual measurements are
    plotted with gray crosses.  and binned photometry are plotted with points
    or squares. Best fitted sinusoids are plotted with solid
    lines. {\em Upper}: binned measurements taken in dithering
    position 1 and 3 (red points) and that taken in 2 and 4 (blue
    squares) are plotted with different symbols. They demonstrate same
    trend of modulation. In upper left panel, the green line a sinusoid
    fitted with all parameters freely varying, and the purple line is
    a sinusoid fitted with the period set the same as that of
    F125W. {\em Middle}: sinusoids fitted without using the
    data taken in Orbit \#1. These curves are almost identical to the
    curves plotted in upper panel. {\em Lower}: photometry measured
    with AFEM-added images and best fitted sinul curves. These
    points and curves are also almost identical to those plotted
    in the upper panel.}
  \label{fig:2}
\end{figure*}

@@

@@

\begin{figure*}
  \centering
  \plotone{f3}
  \caption{Normalized light curves for 2M1207 B (upper) and A (lower)
    with filter F125W (left) and F160W (right). Unbinned
  measurements are plotted in gray crosses and binned photometry are
  plotted with red points. Best fitted sinusoids are plotted
  with blue solid lines.}
  \label{fig:3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{f4a}
  \includegraphics[width=0.45\textwidth]{f4b}

  \caption{Distributions for period (left) and amplitude (right) for the light
    curves of F125W and F160W. The bin sizes for the histograms of
    period  and amplitude are
  0.25 hours and 0.5\%, respectively. Histograms are
  normalized to the maxima. In the right panel, Gaussian profiles are fitted to the
  histograms and plotted in solid lines.}
  \label{fig:4}
\end{figure*}

@@

\begin{figure*}
  \centering
    \includegraphics[width=0.45\textwidth]{f5a}
  \includegraphics[width=0.45\textwidth]{f5b}
  \caption{comparison of 2M1207's rotation period and color change
    with brown dwarfs, \bpic{} b, and solar system planets. {\em
      Left}: period vs. mass plot for 2M1207b (red square), solar
    system planets and \bpic{} b (blue squares), and brown dwarfs
    (black circles, gray shade). Final rotation rates for 2M1207b and
    \bpic{} b estimated based on conservation of angular momentum are
    plotted with faint red and blue squares, respectively. The mass of brown dwarfs are assumed
    to be 30 \mjup{}. The gray rectangle that has a $\pm$15 \mjup
    range in $x$, and a $\pm \sigma$ of brown dwarf periods range in
    $y$, indicates a region where brown dwarfs most likely to appear
    in this diagram. Rotation period monotonically decreases with the
    increase of mass. {\em Right}: ratio of modulation amplitude in J
    and H band vs. spectral type for 2M1207b and brown dwarfs. The
    point for 2M1207b is shifted to +$x$ for half spectral type for
    clarification.  The colors of the points represent J$-$H
    magnitude, and the sizes of the points are proportional to the
    J-band modulation amplitudes. The gray dashed line is the result
    of a linear fit to these points.  Correlation of J- and
    H-band modulation amplitude ratio and spectral type is shown.}
 \label{fig:5}
\end{figure*}

@@

An important result of our study is the direct measurement of the
photometric modulation period of a directly imaged planetary-mass
object. We infer the rotation period of 2M1207b to be the same as the
period of photometric variation. Although horizontal winds can cause
the measured period to differ from true rotation period, it is
unlikely that the difference is greater than the uncertainty of the
measurement, since for Jupiter and Saturn, typical wind speeds are
more than one order of magnitude smaller than the equatorial rotation
speeds.  In the left panel of Figure~\ref{fig:5} we compare the
rotation period of 2M1207b to the solar system planets, \bpic{} b the
only other directly imaged planet with an estimated period and
measured \vsini, and field brown dwarfs from the study of
\cite[][]{Metchev2015}. \citet[][]{Snellen2014} measured \vsini{} for
\bpic{} b and demonstrated that it fits a trend defined by Solar
System planets in which more massive planets have faster rotation
rates. The interesting finding that \bpic{} b, an exoplanet that
formed in a protoplanetary disk, follows this trend suggests a
possibly connection between planet mass, initial angular momentum, and
formation in a disk.

Excitingly, our measurement of the rotation period of 2M1207b, a
planet mass companion that has similar age to \bpic{} b, has a
rotation period that fits in the same trend, as well as majority of
the brown dwarfs. As 2M1207b and \bpic{} b evolve and cool down, they are
expected to shrink to the size of Jupiter. Order of magnitude
estimation based on the conservation of angular momentum results in
final rotation periods of $\sim 5$ h and $\sim 3$ hours
\citep{Snellen2014} for 2M1207b and \bpic{} b, respectively, which
still fit to the period vs. mass trend. Although 2M1207A is known to
host a circumsubstellar disk \citep{Sterzik2004}, the low mass of
typical brown dwarf disks \citep[e.g.]{Klein2003, Mohanty2013} and its
large separation argue against the possibility that 2M1207b has formed
in a protoplanetary disk.  The result that objects formed in different
scenarios share the same trend of period vs. mass suggests that
rotation periods -- in absence of well-determined ages -- may
contribute insufficient evidence for a formation in a disk vs. in a
cloud core environment. Although rotation rates may have limited value
for deciphering formation pathways, measurements of mass, age, and
rotation periods will map the angular momentum evolution of
planetary-mass objects and may place powerful constraints on the
evolution of the internal structures of these contracting objects.

@@

@@

Support for program number 13418 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the
Association of Universities for Research in Astronomy, Inc., under
NASA contract NAS5-26555. The results reported herein benefited from
collaborations and/or information exchange within NASA's Nexus for
Exoplanet System Science (NExSS) research coordination network
sponsored by NASA's Science Mission Directorate. M.S.M. acknowledges
support from the NASA Astrophysics Theory Program. A.P.S. acknowledges
support from NSF grant AST1313444.
%\bibliography{ref.bib}

\begin{thebibliography}{42}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{Ackerman \& Marley(2001)}]{Ackerman2001}
Ackerman, A.~S. \& Marley, M.~S. 2001, ApJ, 556, 872

\bibitem[{{Allard} {et~al.}(2012)}]{Allard2012}
{Allard}, et al. 2012, Royal Society of London
  Philosophical Transactions Series A, 370, 2765

\bibitem[{Apai {et~al.}(2013)}]{Apai2013}
Apai, D., et al. 2013, ApJ, 768, 121

\bibitem[{{Baraffe} {et~al.}(2003)}]{Baraffe2003}
{Baraffe}, I., {Chabrier}, G., {Barman}, T.~S., {Allard}, F., \& {Hauschildt},
  P.~H. 2003, \aap, 402, 701

\bibitem[{{Barman} {et~al.}(2011)}]{Barman2011b}
{Barman}, T.~S., et al. 2011,
  \apjl, 735, L39

\bibitem[{Berta {et~al.}(2012)}]{Berta2012}
Berta, Z.~K., Charbonneau, D., D\'{e}sert, J.-M., {et~al.} 2012, ApJ, 747, 35

\bibitem[{Biretta(2014)}]{Biretta2014}
Biretta, J. 2014, Space Telescope WFC Instrument Science Report, 1, 10

\bibitem[{Bonnefoy {et~al.}(2014)}]{Bonnefoy2014}
Bonnefoy, M., Chauvin, G., et al. 2014, A\&A, 562, A127

\bibitem[{Buenzli {et~al.}(2012)}]{Buenzli2012}
Buenzli, E., Apai, D., et al. 2012, ApJ, 760, L31

\bibitem[{Buenzli {et~al.}(2015)}]{Buenzli2015}
Buenzli, E., Saumon, D., et al. 2015, ApJ, 798, 127

\bibitem[{Burrows {et~al.}(2006)}]{Burrows2006a}
Burrows, A., Sudarsky, D., \& Hubeny, I. 2006, ApJ, 640, 1063

\bibitem[{{Chauvin} {et~al.}(2004)}]{Chauvin2004}
{Chauvin}, G., {Lagrange}, A.-M., et al. 2004, \aap, 425, L29

\bibitem[{{Chauvin} {et~al.}(2005)}]{Chauvin2005}
---. 2005, \aap, 438, L25

\bibitem[{{Currie} {et~al.}(2011)}]{Currie2011}
{Currie}, T., {Burrows}, A., {Itoh}, Y., et al. 2011, \apj, 729, 128

\bibitem[{Dressel(2012)}]{dressel2012wide}
Dressel, L. 2012, Wide Field Camera 3, HST Instrument Handbook, 1

\bibitem[{Ducourant {et~al.}(2008)}]{Ducourant2008}
Ducourant, C., Teixeira, R., et al. 2008, \aap, 477, L1

\bibitem[{{Heinze} {et~al.}(2015)}]{Heinze2015}
{Heinze}, A.~N., {Metchev}, S., \& {Kellogg}, K. 2015, \apj, 801, 104

\bibitem[{Helling {et~al.}(2008)}]{Helling2008}
Helling, C., Ackerman, A., Allard, F., et al. 2008,
  MNRAS, 391, 1854

\bibitem[{{Klein} {et~al.}(2003)}]{Klein2003}
{Klein}, R., {Apai}, D., {Pascucci}, I., {Henning}, T., \& {Waters},
  L.~B.~F.~M. 2003, \apjl, 593, L57

\bibitem[{{Kostov} \& {Apai}(2013)}]{Kostov2013}
{Kostov}, V. \& {Apai}, D. 2013, \apj, 762, 47

\bibitem[{Kreidberg {et~al.}(2014)}]{Kreidberg2014}
Kreidberg, L., Bean, J.~L., D\'{e}sert, J.-M., {et~al.} 2014, Nature, 505, 69

\bibitem[{Krist(1995)}]{Krist1995}
Krist, J. 1995, in Astronomical Data Analysis Software and Systems IV, Vol.~77,
  349

\bibitem[{{MacKenty} {et~al.}(2008)}]{Mackenty2008}
{MacKenty}, J.~W., {Kimble}, R.~A., {O'Connell}, R.~W., \& {Townsend}, J.~A.
  2008,  Vol. 7010,  SPIE
  Conference Series, 1

\bibitem[{{Madhusudhan} {et~al.}(2011)}]{Madhusudhan2011}
{Madhusudhan}, N., {Burrows}, A., \& {Currie}, T. 2011, \apj, 737, 34

\bibitem[{Mandell {et~al.}(2013)}]{Mandell2013}
Mandell, A.~M., Haynes, K., Sinukoff, E., {et~al.} 2013, ApJ, 779, 128

\bibitem[{{Marley} {et~al.}(2012)}]{Marley2012}
{Marley}, M.~S., {Saumon}, D., et al. 2012, \apj, 754, 135

\bibitem[{{Marley} {et~al.}(2010)}]{Marley2010}
{Marley}, M.~S., {Saumon}, D., \& {Goldblatt}, C. 2010, \apjl, 723, L117

\bibitem[{Marois {et~al.}(2008)}]{Marois2008a}
Marois, C., Macintosh, B., et al. 2008, Science, 322, 1348

\bibitem[{Metchev {et~al.}(2015)}]{Metchev2015}
Metchev, S.~A., Heinze, A., et al. 2015, ApJ, 799, 154

\bibitem[{{Mohanty} {et~al.}(2013)}]{Mohanty2013}
{Mohanty}, S., {Greaves}, J., et al. 2013, \apj, 773,
  168

\bibitem[{Mohanty {et~al.}(2007)}]{Mohanty2007}
Mohanty, S., Jayawardhana, R., Huelamo, N., \& Mamajek, E. 2007, ApJ, 657, 1064

\bibitem[{Patience {et~al.}(2010)}]{Patience2010}
Patience, J., King, R.~R., {De Rosa}, R.~J., \& Marois, C. 2010, A\&A, 517, A76

\bibitem[{Radigan {et~al.}(2012)}]{Radigan2012}
Radigan, J., Jayawardhana, R., Lafreni\`{e}re, D., Artigau, E., Marley, M., \&
  Saumon, D. 2012, ApJ, 750, 105

\bibitem[{{Showman} \& {Kaspi}(2013)}]{Showman2013}
{Showman}, A.~P. \& {Kaspi}, Y. 2013, \apj, 776, 85

\bibitem[{{Skemer} {et~al.}(2011)}]{Skemer2011}
{Skemer}, A.~J., {Close}, L.~M., et al. 2011, \apj, 732, 107

\bibitem[{{Skemer} {et~al.}(2012)}]{Skemer2012}
{Skemer}, A.~J., {Hinz}, P.~M., {Esposito}, S., {Burrows}, A., {et~al.} 2012,
  \apj, 753, 14

\bibitem[{Snellen {et~al.}(2014)}]{Snellen2014}
Snellen, I. A.~G., Brandl, B.~R., et al. 2014, Nature, 509, 63

\bibitem[{Song {et~al.}(2006)}]{Song2006}
Song, I., Schneider, G., et al. 2006, ApJ, 652, 724

\bibitem[{{Sterzik} {et~al.}(2004)}]{Sterzik2004}
{Sterzik}, M.~F., {Pascucci}, I., {Apai}, D., {van der Bliek}, N., \&
  {Dullemond}, C.~P. 2004, \aap, 427, 245

\bibitem[{{Yang} {et~al.}(2015)}]{Yang2015}
{Yang}, H., {Apai}, D., et~al. 2015, \apjl, 798, L13

\bibitem[{{Zhang} \& {Showman}(2014)}]{Zhang2014}
{Zhang}, X. \& {Showman}, A.~P. 2014, \apjl, 788, L6

\end{thebibliography}

\end{document}
